### 2018-04-11 paper.Rmd

```{r load_packages, echo = FALSE, warning=FALSE}
library(papaja)
library(tidyverse)
library(childesr)
library(directlabels)
library(here)
knitr::opts_chunk$set(cache = TRUE, echo = FALSE)
```

@@

1. introduce the research question
2. allow students to reflect or do a pair-and-share discussion with their neighbor
3. show the trajectory of a single lexical item while explaining the key parts of the visualization (see Panel A of Figure \ref{fig:in-class-demo-plot})
4. elicit hypotheses from students about the kinds of words that children are likely to produce 
5. make real-time queries to the web applications to add students' suggestions and talk through the updated plots (Panels B and C of Figure \ref{fig:in-class-demo-plot})
6. finish by entering a pre-selected set of words that communicate the critical takeaway (Panel D of Figure \ref{fig:in-class-demo-plot})

```{r in-class-demo-plot, fig.pos="h", out.width = "100%", fig.cap="Worked example of using the web applications for in-class teaching. Panels A-D show how an instructor could dynamically build a plot during a lecture to interactively demonstrate a key concept in language acquisition."}
library(here)
library(png)
png::readPNG(here::here("imgs/in_class_teach_viz.png")) %>% grid::grid.raster()
```

In addition to the web applications, instructors can use childes-db to download the raw data used to generate the figures. This allows teachers an opportunity to have students further explore and analyze the data they see in the plots. Moreover, this functionality provides an example of another way childes-db can facilitate language acquisition courses by making data easily-accessible for tutorials and student research projects.

### Tutorials and assignments

One of the goals for courses on applied natural language processing (NLP) is for students to get hands-on experience using state of the art NLP tools to analyze real-world language data [@hearst2005teaching]. A primary challenge for the instructor is to decide how much time should be spent teaching the requisite programming skills for accessing and formatting language data, which are typically unstructured. One pedagogical strategy is to abstract away these details and avoid having students deal with obtaining data and formatting text. This approach shifts students' effort away from data cleaning and towards programming analyses that encourage students to explore language data and test interesting hypotheses.

One goal of childes-db and `childesr` API is to provide instructors with an easy-to-learn method for giving students programmatic access to CHILDES data. This will reduce the time spent getting data out of CHILDES and allow more time for thinking about interesting questions that can be answered with NLP and child language data. Second, by writing our API in the R programming language, students will gain access to a general workflow can be integrated into a pipeline that includes the newest NLP tools.

For example, an instructor could create a programming assignment with the goal of reproducing the key findings in the case studies presented above -- color words or gender. Depending on the students' knowledge of R, the instructor could decide how much of the `childesr` starter code to provide before asking students to generate their own plots and writeups. Moreover, the instructor could take advantage of recent advances in tools for teaching literate programming such as R Markdown [@xie2015dynamic; @baumer2014r], building in pre-written blocks of executable code that demonstrate key programming concepts for students and including incomplete or blank code blocks that students can use to write their own code.

>>>>

```{r load_packages, echo = FALSE, warning=FALSE}
library(papaja)
library(tidyverse)
library(childesr)
library(directlabels)
library(koRpus)
library(png)
library(here)
knitr::opts_chunk$set(cache = TRUE, echo = FALSE)
```

@@

1. introduce the research question (e.g., What are the types of words that children first produce?)
2. allow students to reflect or do a pair-and-share discussion with their neighbor
3. show the trajectory of a single lexical item while explaining key parts of the visualization (see Panel A of Figure \ref{fig:in-class-demo-plot})
4. elicit hypotheses from students about the kinds of words that children are likely to produce 
5. make real-time queries to the web application to add students' suggestions and talk through the updated plots (Panels B and C of Figure \ref{fig:in-class-demo-plot})
6. finish by entering a pre-selected set of words that communicate the important takeaway point (Panel D of Figure \ref{fig:in-class-demo-plot})

```{r in-class-demo-plot, fig.pos="h", out.width = "95%", fig.cap="Worked example of using the web applications for in-class teaching. Panels A-D show how an instructor could dynamically build a plot during a lecture to demonstrate a key concept in language acquisition."}

png::readPNG(here::here("imgs/in_class_teach_viz.png")) %>% grid::grid.raster()
```

In addition to the web applications, instructors can use childes-db to download the raw data used to generate the figures. This gives students the opportunity to further explore and analyze the data they see in the plots. Moreover, this functionality provides an example of a second way that childes-db can facilitate language acquisition courses by making data easily-accessible for tutorials and student research projects.

### Tutorials and programming assignments

One of the goals for courses on applied natural language processing (NLP) is for students to get hands-on experience using NLP tools to analyze real-world language data. A primary challenge for the instructor is to decide how much time should be spent teaching the requisite programming skills for accessing and formatting language data, which are typically unstructured. One pedagogical strategy is to abstract away these details and avoid having students deal with obtaining data and formatting text. This approach shifts students' effort away from data cleaning and towards programming analyses that encourage the exploration and testing of interesting hypotheses.

One goal of childes-db and `childesr` API is to provide instructors with an easy-to-learn method for giving students programmatic access to child language data. The aim is to reduce time spent getting data out of CHILDES and allow more course time for thinking about interesting questions that could be answered with NLP and child language data. Moreover, by writing our API in the R programming language, students will gain access to a general workflow can be integrated into an analysis pipeline that includes state of the art NLP tools.

For example, an instructor could create a programming assignment with the goal of reproducing the key findings in the case studies presented above -- color words or gender. Depending on the students' knowledge of R, the instructor could decide how much of the `childesr` starter code to provide before asking students to generate their own plots and writeups. Moreover, the instructor could take advantage of recent advances in tools for teaching literate programming such as R Markdown [@xie2015dynamic], building in pre-written blocks of executable code that demonstrate key programming concepts for students and including incomplete or blank code blocks that students can use to write their own code.
